cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added gen_conicspiral

>>>>

The `gen_conicspiral(n, p, spins)` function generates a dataset of $n$ points forming a conical spiral in the first four dimensions of a $p$-dimensional space. The geometry combines radial expansion, vertical elevation, and spiral deformation, simulating a structure that fans out like a $3\text{-}D$ conic helix.

The shape is defined by parameter $\theta \in [0, 2\pi \cdot \text{spins}]$, controlling the angular progression of the spiral. The mapping to Cartesian space is as follows:

The Archimedean spiral in the horizontal plane is represented by;

$X_1 = \theta \cdot \cos(\theta)$ for radial expansion in x.
$X_2 = \theta \cdot \sin(\theta)$ for radial expansion in y.

The growth pattern resembles a cone, with the height increasing according to $X_3 = 2 \cdot \theta / \max(\theta) + \varepsilon_3$, with $\varepsilon_3 \sim \mathcal{U}(-0.1, 0.6).$

Spiral modulation in the fourth dimension is represented by $X_4 = \theta \cdot \sin(2\theta) + \varepsilon_4$, with $\varepsilon_4 \sim \mathcal{U}(-0.1, 0.6)$ which simulates a twisting helical component in a non-radial dimension.

This results in a $3\text{-}D$ spiral surface expanding upward and outward like a cone, with an oscillatory fourth dimension capturing spiral irregularities.

For $p > 4$, the dataset includes isotropic Gaussian noise in the remaining dimensions via `gen_noisedims()`:

$$
X\_j \sim \mathcal{N}(0, 0.05^2), \quad j = 5, \dots, p.
$$
